
\documentclass{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\begin{document}

\section*{\uppercase{SURVEY QUESTIONNAIRE}}\label{sec:appendix}
Questions with standard bullets ($\bullet$) are single-select while questions
with square ($\square$) are multi-select.

1) What is your age? $\bullet $ Under 18  $\bullet $ 18-23  $\bullet $ 24-29  $\bullet $ 30 and above

2) What is your gender? $\bullet $ Male $\bullet $ Female $\bullet $ Non-binary $\bullet $ Prefer to self-describe [Text field] $\bullet $ Prefer not to say

3) What is your ethnic group? $\bullet $ Han $\bullet $ Other [Text field] $\bullet $ Prefer not to say

4) What subject are you studying in the last semester? $\bullet $ Computer Architecture $\bullet $ Electronics and IoT $\bullet $ Automation and Embedded Systems $\bullet $ Other [Text field]

5) What year of study are you in? $\bullet $ First Year $\bullet $ Second Year $\bullet $ Third Year $\bullet $ Fourth Year

6) How would you rate the difficulty of understanding theoretical concepts in your computing courses?
$\bullet $ Very Easy $\bullet $ Easy $\bullet $ Moderate $\bullet $ Difficult $\bullet $ Very Difficult

7) How challenging do you find applying theoretical knowledge to practical tasks in your computing courses?
$\bullet $ Very Easy $\bullet $ Easy $\bullet $ Moderate $\bullet $ Difficult $\bullet $ Very Difficult

8) Please select exactly three barriers you believe have the greatest impact on your computing courses. If your answers are not among the options, please add them below.

$\square$ Language barriers in understanding course material

$\square$ Insufficient prior knowledge of key computing concepts

$\square$ Difficulty in grasping abstract theoretical concepts

$\square$ Challenges due to cultural differences in learning environments

$\square$ Unclear explanations of the knowledge from lecturers

$\square$ Lack of practical examples in the course material

$\square$ Inadequate lab facilities or hands-on practice opportunities

$\square$ Limited access to necessary technology or software

$\square$ The inappropriate assessment of the course (e.g. the weights of theory and practice are unreasonable.)

$\square$ The improper course content composition, such as having much theory and not much practical content

$\square$ Peer collaboration or group work challenges

$\square$ Other [Text field]

9) To what extent does the chosen barrier 1 affect your learning?
$\bullet $ Not at all $\bullet $ Slightly $\bullet $ Moderately $\bullet $ Very $\bullet $ Extremely

10) To what extent does the chosen barrier 2 affect your learning?
$\bullet $ Not at all $\bullet $ Slightly $\bullet $ Moderately $\bullet $ Very $\bullet $ Extremely

11) To what extent does the chosen barrier 3 affect your learning?
$\bullet $ Not at all $\bullet $ Slightly $\bullet $ Moderately $\bullet $ Very $\bullet $ Extremely

12) What was your level of experience in computing before entering the current course?
$\bullet $ No Experience $\bullet $ Beginner $\bullet $ Intermediate $\bullet $ Expert

[If you selected 'Beginner,' 'Intermediate,' or 'Expert,' please answer Question 13A).:]

13A) To what extent do you think your previous computing experience has helped you perform well in these courses?
$\bullet $ Not at all $\bullet $ Slightly $\bullet $ Moderately $\bullet $ Very $\bullet $ Extremely

14) How engaged are you in your computing courses?
$\bullet $ Not at all $\bullet $ Slightly $\bullet $ Moderately $\bullet $ Very $\bullet $ Extremely

[If you selected any option other than 'Not at all', please answer Question 15A):]

15A) Do you think your level of participation in the course affects your learning and helps you overcome learning barriers?
$\bullet $ Strongly disagree $\bullet $ Disagree $\bullet $ Neutral $\bullet $ Agree $\bullet $ Strongly agree

16) To what extent has the support you received from the lecturer and teaching assistant helped you overcome obstacles?
$\bullet $ Not at all $\bullet $ Slightly $\bullet $ Moderately $\bullet $ Very $\bullet $ Extremely

17) How has transitioning from the Chinese educational system to the New Zealand educational system affected your learning experience and outcomes?
$\bullet $ Negative $\bullet $ Slightly negative $\bullet $ Neutral $\bullet $ Slightly positive $\bullet $ Positive

18) What aspects do you think can be further improved in these courses that have both theoretical and practical components? Please provide as much detail as possible. [Open-ended question. Participants were allowed to write without any word limit.]

19) Do your interests and career aspirations fall into the computing/computer science field?
$\bullet $ Strongly disagree $\bullet $ Disagree $\bullet $ Neutral $\bullet $ Agree $\bullet $ Strongly agree

[If you selected 'Strongly disagree' or 'Disagree' in Question 19), please answer Question 20A):]

20A) Do your parents, relatives, and friends influence your career aspirations?
$\bullet $ Strongly disagree $\bullet $ Disagree $\bullet $ Neutral $\bullet $ Agree $\bullet $ Strongly agree

[If you selected 'Neutral,' 'Agree,' or 'Strongly agree' in Question 19), please answer Question 20B):]

20B) Do your career aspirations align with your interests?
$\bullet $ Strongly disagree $\bullet $ Disagree $\bullet $ Neutral $\bullet $ Agree $\bullet $ Strongly agree

[If you answered Question 20A), please answer Question 21A):]

21A) Because your future career is unrelated to computer technology, do you find it more difficult to participate in this course?
$\bullet $ Strongly disagree $\bullet $ Disagree $\bullet $ Neutral $\bullet $ Agree $\bullet $ Strongly agree

[If you answered Question 20B), please answer Question 21B):]

21B) Does your education in the computing field help motivate you and make it easier to overcome barriers encountered during the course?
$\bullet $ Strongly disagree $\bullet $ Disagree $\bullet $ Neutral $\bullet $ Agree $\bullet $ Strongly agree

22) For courses like this, do you have any specific study strategies or recommendations on learning resources for your juniors? Please provide as much detail as possible. [Open-ended question. Participants were allowed to write without any word limit.]

\end{document}
